Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-22 doc/PRF2022/PRF_main.tex
minor fix by peter

The Results section showed that variations in free energy and strain
generally depend on the distribution of fluid stresses i.e., shear
versus TG flow. To further illustrate how fluid stresses interact with
the geometry of the JP phases, we initialize a circular vesicle bilayer
in various TG-flow cell sizes $\lambda$ ranging from $\lambda=1$ nm in
Figure~\ref{fig:PramChange}(b) to $\lambda=4$ nm in
Figure~\ref{fig:PramChange}(e). As shown in the Supplementary Material,
these JP vesicles fluctuate and deform around a steady shape of an
octagon ($\lambda=1$~nm), a dimpled square ($\lambda=2$~nm), a rounded
diamond ($\lambda=3$~nm), and a rounded rectangle ($\lambda=4$~nm).

>>>>

The Results section showed that variations in free energy and strain
generally depend on the distribution of fluid stresses i.e., shear
versus TG flow. To further illustrate how fluid stresses interact with
the geometry of the JP phases, we initialize a circular vesicle bilayer
in various TG-flow cell sizes $\lambda$ ranging from $\lambda=1$ nm in
Figure~\ref{fig:PramChange}(b) to $\lambda=4$ nm in
Figure~\ref{fig:PramChange}(e). As shown in the Supplementary Material Movie S6,
these JP vesicles fluctuate and deform around a steady shape of an
octagon ($\lambda=1$~nm), a dimpled square ($\lambda=2$~nm), a rounded
diamond ($\lambda=3$~nm), and a rounded rectangle ($\lambda=4$~nm).

### 2023-03-22 doc/PRF2022/Supplementary.tex
minor fix by peter

\noindent
{\bf Movie S6. Single Vesicle in a Taylor-Green Flow with Various $\lambda$ Values} 
The parameter $\lambda$ controls the cell size in Taylor-Green flow. 
$\lambda$ values are varied from 1.0 to 4.0 while the flow rate $\lambda\dot\gamma=0.1$ is fixed. There is a rotation transition from counterclockwise ($\lambda=1$ nm and  2 nm) to clockwise ($\lambda=3$ nm and 4 nm). \\

>>>>

\noindent
{\label{MovieS6}\bf Movie S6. Single Vesicle in a Taylor-Green Flow with Various $\lambda$ Values} 
A circular vesicle bilayer is placed in the Taylor-Green flow. 
The parameter $\lambda$ controls the cell size and the values are varied from 1.0 nm to 4.0 nm while the flow rate $\lambda\dot\gamma=0.1$ is fixed. There is a rotation transition from clockwise ($\lambda=1$ nm and  2 nm) to counterclockwise ($\lambda=3$ nm and 4 nm). Moreover, the resulting steady shapes of all cases are different polygons. We plot the streamlines in the background.\\
